---
title: "Resolution of the "
author: 
  - Fabio
  - Giovanny
date: "21"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```



## Workshop on Reproducible Research 


The first step is to load the data


#### Load data:
```{r}
Scopus=read.csv("Scopus.csv",header = T, stringsAsFactors = FALSE)



```



#### Exercise 1: 

- **Fisheries**: Fisheries and Aquaculture Department of the Food and 
Agriculture Organization of the United Nations collects data on fisheries 
production of countries. [This Wikipedia page](https://en.wikipedia.org/wiki/Fishing_industry_by_country) 
lists fishery production of countries for 2005. For each country tonnage from 
capture and aquaculture are listed. Note that countries which harvested less 
than 100,000 tons are not included in the data. The source data can be found 
in the `fisheries` dataset in the **dsbox** package. The following plots were 
produced based off the data given on the Wikipedia page.


```{r ex1}

```

#### Exercise 2: 

- **Instructional staff employee trends**: The American Association of 
University Professors (AAUP) is a nonprofit membership association of faculty 
and other academic professionals. 

[This report](https://www.aaup.org/sites/default/files/files/AAUP_Report_InstrStaff-75-11_apr2013.pdf) 
compiled by the AAUP shows trends in instructional staff employees between 1975 and 2011.

The following plots were produced based off the data given on the Wikipedia page.



```{r ex2}

```

